### 2021-07-14 ch/7-discussion.tex
I can't believe I managed to write something for this

The remainder of this chapter is split into three parts:
In \secref{sec:ch7-limitations},
I discuss some of the limitations of the presented methods to keep in mind,
and what the goal of the applications of the methods should be.
\Secref{sec:potential-extentions} is about ways in which the work could be extended,
and \secref{sec:broader-perspective} discusses the broader perspective of this topic,
including a wider discussion of the future of \acl{ML}.

@@

% ============ price of fairness ==========
% ==============

% ============ does your method help with finding clusters unsupervisedly ==========
% ==============

@@

% ====== why even work with bad data? =====
Now, one possible objection here is:
if those datasets are of such poor quality,
then maybe we just should not train any \ac{ML} model on these and should not use them to make automated decisions?
While this question is mostly beyond the scope of this document, let me offer some thoughts on this:
It is true that even after the application of de-biasing techniques,
the resulting models still should not be fully trusted,
but they can still ease the burden of checking everything manually;
similar to an email spam filter which is not perfect, but still very useful.
Or, put another way, it is always important to check what the realistic alternative is;
we should not compare a model to a non-existing perfect ideal, but to the actual solution that would be used instead.
One could imagine a hybrid approach where an automated system makes preliminary decisions,
but random samples are reviewed by humans and decisions can always be challenged.
Ideally, the model itself would tell us about decisions it is uncertain about.

@@

\section{Potential extensions}\label{sec:potential-extentions}
%
% ======= potential technical improvements ======
There are also certain technical improvements that could be made.
In general, it would be desirable to have more theoretical bounds on performance.
This likely involves specifying the requirements for the algorithms more precisely.
% which is also useful information for potential users.
The method based on target labels would furthermore benefit from better-calibrated probability outputs.
\acf{GP} classifiers show generally good calibration,
but cannot be easily applied in domains where deep neural networks are used.
On the other hand, neural networks are known to be overconfident
\citep[especially when using ReLU activations;][]{hein2019relu},
so to apply the proposed method to images directly is not straightforward.
The other two proposed methods would benefit from improved adversarial training procedures.
Training these models is not straightforward as the losses have to be balanced
and in some cases, the update schedule needs to be changed.
Both the calibration of neural networks and the stability of adversarial training
are issues that are widely recognised in the \ac{ML} community,
so there is hope that progress will be made on these.
% ==============

>>>>

The remainder of this chapter is split into three parts:
In \secref{sec:ch7-limitations},
I discuss some of the limitations of the presented methods to keep in mind,
and what the goal of the applications of the methods should be.
\Secref{sec:potential-extentions} is about ways in which the work could be extended,
and \secref{sec:broader-perspective} discusses the broader perspective of this topic,
including a wider discussion of the future of the field.

@@

% ============ price of fairness ==========
It also should be mentioned here that compared to training straightforward, bias-unaware classifiers,
the sampling-bias-targeting methods (\ie, the second and the third method)
incur additional costs in terms of computing resources, training time and human labour.
This label-bias-targeting method (\ie, the first one) only impacts the computation of the loss
and does not require additional training data,
so it has a negligible impact training cost.
The second method is the most costly
as the training of \acp{INN} requires a large amount of memory and compute
because \acp{INN} only \emph{transform} the (very high-dimensional) inputs
and never perform anything like the lossy compression that other neural network do.
Furthermore, the method requires additional data with \(s\) labels.
Still, if the additional training cost enables the use of data
that was previously unusable due to strong spurious correlations,
then it can still be worthwhile,
and it is also important to keep in mind that a model can be trained once
and then used millions of times.
This has to be decided on a case-by-case basis,
and unfortunately means that these de-biasing methods will likely not be use prophylactically,
but only if there is an explicit expectation of harm otherwise.
% ==============

@@

% ====== why even work with bad data? =====
Now, one possible objection here is:
if those datasets are of such poor quality,
then maybe we just should not train any \ac{ML} model on these and should not use them to make automated decisions.
While this question is mostly beyond the scope of this document, let me offer some thoughts on this:
It is true that even after the application of de-biasing techniques,
the resulting models still should not be fully trusted,
but they can still ease the burden of tedious manual labour;
similar to an email spam filter which is not perfect, but still very useful.
Or, put another way, it is always important to check what the realistic alternative is;
we should not compare a model to a non-existing perfect ideal, but to the actual solution that would be used instead.
One could imagine a hybrid approach where an automated system makes preliminary decisions,
but random samples are reviewed by humans and decisions can always be challenged.
Ideally, the model itself would tell us about decisions it is uncertain about.

@@

% ============ does your method help with finding clusters unsupervisedly ==========
% I think by "cluster" he means demographic group
% the answer is 'no' :(
The last limitation to mention is that throughout the thesis,
the assumption is made that all relevant `demographic groups' (or `environments' or `subgroups')
are known, or at least that it is known how \emph{many} groups there are.
This goes back to the argument above that no \emph{completely general} method can exist to solve dataset bias;
there has to be \emph{some} inductive bias in order to be able to learn anything.
There have been attempts in the literature to address this,
like \citet{HasSriNamLia18} (see \secref{sec:groundtruth-centric-view-of-bias}),
which only requires knowledge of a lower bound on the size of groups in the given data.
Such an assumption could potentially replace the assumption of knowing the \emph{number} of groups
(as we assume for the third method presented).
The other direction to go in is to give up on groups altogether and try to enforce \emph{individual fairness}.
However, this has its own set of problems,
the foremost of which is requiring a sensible distance function.
% ==============

\section{Potential extensions}\label{sec:potential-extentions}
%
% ======= potential technical improvements ======
% There are also certain technical improvements that could be made.
In general, it would be desirable to have more theoretical bounds on performance.
This likely involves specifying the requirements for the algorithms more precisely.
% which is also useful information for potential users.
The method based on target labels would furthermore benefit from better-calibrated probability outputs.
\acf{GP} classifiers show generally good calibration,
but cannot be easily applied in domains where deep neural networks are used.
On the other hand, neural networks are known to be overconfident
\citep[especially when using ReLU activations;][]{hein2019relu},
so to apply the proposed method to images directly is not straightforward.
The other two proposed methods would benefit from improved adversarial training procedures.
Training these models is not straightforward as the losses have to be balanced
and in some cases, the update schedule needs to be changed.
Both the calibration of neural networks and the stability of adversarial training
are issues that are widely recognised in the \ac{ML} community,
so there is hope that progress will be made on these.
% ==============
